---
title: "About"
---

Welcome to the [effective data visualisation with R]{style="color:#006DAE;"} workshop!


<i class="fas fa-calendar" style="width:40px;"></i>  Tuesday 6th December 2022  
<i class="fas fa-clock" style="width:40px;"></i>   9.00AM - 12.00PM AEDT  
<i class="fas fa-map-pin" style="width:40px;"></i>  Zoom (links provided to participants via email)

## Materials

All materials are hosted on a GitHub repo [here](https://github.com/emitanaka/EDVR-workshop) and can be downloaded [here as a zip file](https://github.com/emitanaka/EDVR-workshop/archive/refs/heads/master.zip) (including the website, slides and exercises).

Once the material is downloaded, open the `docs/index.html` in a browser to see this website ([emitanaka.org/EDVR-workshop](https://emitanaka.org/EDVR-workshop/)). 



## Schedule


## Installation

This is only needed if the exercise links above do not work for you.

```{r}
#| eval: false
install.packages(c("remotes", "learnr"))
remotes::install_github("emitanaka/EDVR-workshop/pkg")
```


## Exercises 


To run the exercises locally, install the packages under [Installation](#installation) and then run:

```{r}
#| eval: false
learnr::run_tutorial("exercise-01", package = "edvr.workshop")
learnr::run_tutorial("exercise-02", package = "edvr.workshop")
```

